\documentclass[10pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amssymb} % for checkboxes
\usepackage[a4paper, top=0.75in, left=1in, right=1in, bottom=1in]{geometry} % Adjusts the margins
\usepackage{tikz}


\title{STEM Camp: Brain Master Project Survey}
\author{STEM Camp Team}
\date{}

\begin{document}

\maketitle

\section*{Demographic Information}

Please fill out the following demographic information:

\begin{enumerate}
    \vspace{3mm}
    \item Name: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    \vspace{2mm}
    \item Age: \_\_\_ years
    \vspace{2mm}
    \item Grade: \_\_\_
    \vspace{2mm}
    \item Gender: $\square$ Male $\square$ Female $\square$ Other $\square$ Prefer not to say
    \vspace{2mm}
    \item Do you have previous experience with coding or programming? $\square$ Yes $\square$ No
    \vspace{2mm}
\end{enumerate}

\section*{Pre-Survey: Baseline Interest in STEM}

Respond to each statement by marking the circle that best describes your level of agreement:
\vspace{3mm}

Legend: $\circ$ Strongly Disagree | $\circ$ Disagree | $\circ$ Neutral | $\circ$ Agree | $\circ$ Strongly Agree

\begin{enumerate}[label=\arabic*.]
    \vspace{3mm}
    \item I understand what STEM (Science, Technology, Engineering, Mathematics) involves. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I have previously used an Arduino, ESP32, or another micro-controller. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I am interested in learning more about technology and engineering. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item My favorite subject in school is science or math. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I have participated in technology or engineering projects before this one. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I believe that technology can solve significant global problems. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I am excited about participating in the Brain Master project. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I feel confident in my ability to complete technical projects like Brain Master. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I expect to achieve meaningful learning outcomes from participating in this project. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I anticipate challenges in completing this project but am prepared to tackle them. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}

\end{enumerate}

\end{document}
