\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amssymb} % for checkboxes
\usepackage[a4paper, top=1in, left=1in, right=1in, bottom=1in]{geometry}

\title{UNLV Vegas STEM Camp: Project Survey}
\author{Dr. SJ and Robert Pearce}
\date{}

\begin{document}

\maketitle

\section*{Demographic Information}

Please fill out the following demographic information:

\begin{enumerate}
    \item Age: \_\_\_ years
    \item Grade: \_\_\_
    \item Gender: $\square$ Male $\square$ Female $\square$ Other $\square$ Prefer not to say
    \item Do you have previous experience with coding or programming? $\square$ Yes $\square$ No
\end{enumerate}

\section*{Pre-Survey: Baseline Interest in STEM}

Please answer the following questions to help us understand your initial interest in STEM (Science, Technology, Engineering, and Mathematics).

\begin{enumerate}
    \item What do you already know about STEM?
    \vspace{30mm}
    \item Have you ever used an Arduino, ESP32, or any other microcontroller before? $\square$ Yes $\square$ No
    \vspace{10mm}
    \item On a scale from 1 (not interested at all) to 5 (extremely interested), how interested are you in learning about technology and engineering? \\
          1 $\square$ 2 $\square$ 3 $\square$ 4 $\square$ 5
    \vspace{10mm}
    \item What is your favorite subject in school and why?
    \vspace{30mm}
    \item Have you participated in any technology or engineering projects before? $\square$ Yes $\square$ No
    \vspace{10mm}
    \newpage
    \item Do you think technology can help solve important problems in the world? Why or why not?
    \vspace{30mm}
    \item What are you most excited to learn about in this project?
    \vspace{10mm}
    \item How confident are you in your ability to build something with technology like an ESP32? \\
          $\square$ Not confident \\
          $\square$ Somewhat confident \\
          $\square$ Neutral \\
          $\square$ Confident \\
          $\square$ Very confident
    \vspace{10mm}
    \item What do you hope to achieve by participating in this camp?
    \vspace{30mm}
    \item What do you think will be your biggest challenge in this camp?
    
\end{enumerate}

\end{document}
