\documentclass[10pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amssymb} % for checkboxes
\usepackage[a4paper, top=0.75in, left=1in, right=1in, bottom=1in]{geometry} % Adjusts the margins
\usepackage{tikz}

\title{STEM Camp: Brain Master Project Survey}
\author{STEM Camp Team}
\date{}

\begin{document}

\maketitle

\section*{Demographic Information}

Please fill out the following demographic information:

\begin{enumerate}
    \vspace{3mm}
    \item Name: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    \vspace{2mm}
    \item Age: \_\_\_ years
    \vspace{2mm}
    \item Grade: \_\_\_
    \vspace{2mm}
    \item Gender: $\square$ Male $\square$ Female $\square$ Other $\square$ Prefer not to say
    \vspace{2mm}
    \item Do you have previous experience with coding or programming? $\square$ Yes $\square$ No
    \vspace{2mm}
\end{enumerate}

\section*{Post-Survey: Reflecting on the Brain Master Project}

Respond to each statement by marking the circle that best describes your level of agreement:
\vspace{3mm}


Legend: $\circ$ Strongly Disagree | $\circ$ Disagree | $\circ$ Neutral | $\circ$ Agree | $\circ$ Strongly Agree

\begin{enumerate}[label=\arabic*.]
    \vspace{3mm}
    \item Participating in the Brain Master project has increased my interest in STEM. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I enjoyed working with the Arduino and ESP32 during the project. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item My understanding of how technology functions has improved significantly. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I have acquired new skills through this project that I can apply in other areas. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item The project met my expectations in terms of difficulty and complexity. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item I am more likely to participate in future STEM projects because of this experience. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item The most interesting aspect of the project provided significant learning. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item The skills I learned in this project are applicable to solving real-world problems. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item This project has influenced my consideration of a career in a STEM field. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}
    
    \item The Brain Master project could be improved for future participants. \hfill $\circ$ $\circ$ $\circ$ $\circ$ $\circ$
    \vspace{3mm}

\end{enumerate}

\end{document}
